---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Marcus Minko"
date: "02-28-2022"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(broom)
library(openintro)
```

### View Data Distribrution

```{r score-distribution}

evals %>% 
  ggplot(aes(x = score)) + geom_histogram (bindwidth = .25, color = "white", fill = "navy") +
  labs(x = "Evalution Score")

evals %>% 
  summarize (mean(score), median(score), min(score), max(score))

# score distribution is somewhat left-skewed; in general, students give pretty scores

evals %>% 
  ggplot(aes(x = score, y = bty_avg)) + 
  geom_point() + 
  labs(y = "Beauty Rating", x = "Evalution Score")
         
evals %>% 
  ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() +
  labs(y = "Beauty Rating", x = "Evalution Score")

#The geom_point plot looks like there are fewer data than there actually is

```

### Linear Regression Model

```{r linear-regression}

m_bty = lm(score~bty_avg, data = evals) #Create the linear regression
summary(m_bty)
evals %>% 
ggplot(aes(x=score, y=bty_avg)) + 
  geom_point()+
  geom_smooth(method=lm, 
              linetype="solid") +
  geom_jitter() +
  labs(y = "Beauty Rating", x = "Evalution Score")


#Regression line orange, no shading for error

m_bty = lm(score~bty_avg, data = evals) #Create the linear regression
summary(m_bty)
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point()+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="orange") +
        geom_jitter() +
  labs(y = "Beauty Rating", x = "Evalution Score")

```
score = 3.88 + .07(bty_avg)

Slope = .07, significant p-value. So for every one-unit increase in beauty score, there is a .07 increase in the prof evaluation score

Intercept: For a beauty of zero, you would expect an prof evaluation score of 3.88. This doesn't make much sense, since a score of zero is not possible (scales 1-10)

R-squared = 0.04, beauty rating accounts for 4% of the variance in average professor evaluation scores.

### Regression line & Gender

```{r gender-regression}

m_gen = lm(score~gender, data = evals)
summary(m_gen)

#y= .14(x) + 4.09 
#males: y = .14(0) + 4.09 predicted score for males is 4.09
#females: y = .14(1) + 4.09 predicted score for females is 4.23

m_rank = lm(score~rank, data = evals)
summary(m_rank)

#y= 4.28 -.13(X1) + -.15(X2)
#predicted score for teaching rank is 4.28
#predicted score for tenure track is 4.15
#predicted score for tenured is 4.13
```

### Relevel Rank positions
```{r rank-relevel}

rank_evals <- evals%>%
  mutate(rank_relevel = case_when(rank== "tenure track" ~ 0,
                          rank== "teaching" ~ 1,
                          rank== "tenured" ~ 2))
m_rank_relevel<- lm( score~ rank_relevel, data = rank_evals) #Create the linear regression
summary(m_rank_relevel)

#y = 4.2 - .02(rank)
#each step up the rank is associated with a .02 decrease in prof eval score (non-significant)
#rank only accounts for .001 percent of variance in prof eval score.
```

###Tenure Eligibility
``` {r tenure-eligible}
evals <- evals%>% 
  mutate(tenure_eligible = if_else(rank == "teaching", "No", "Yes"))

#Regression line based on tenure eligibility

m_tenure_eligible = lm(score ~ tenure_eligible, data = evals) 
summary(m_tenure_eligible)

## y = 4.28 -.14(tenure_eligible)
# tenure eligible faculty have predicted prof eval scores .14 lower (4.14) than non-tenure eligible faculty (4.28)
#R-squared: tenure eligibility accounted for .01 percent of the variance in prof evaluation score
```

